---
title: "Analyzing Gapminder data"
author: "Mine Cetinkaya-Rundel"
date: "8/31/2017"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load packages, message=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
```

## Step 1: Load data

```{r Load data}
gapminder <- read_csv("https://stat.duke.edu/~mc301/data/gapminder.csv")
```

## Step 2: Subset data

- Start with the `gapminder` dataset

- Filter for cases (rows) where year is equal to 2007

- Save this new subsetted dataset as `gap07`

```{r Subset data}
gap07 <- gapminder %>%
  filter(year == 2007)
```


## Step 3: Explore and visualize

**Task:** Visualize the relationship between `gdpPercap` and `lifeExp`.

```{r Scatterplot}
ggplot(data = gap07, aes(x = gdpPercap, y = lifeExp)) + 
  geom_point()
```

## Step 4: Dig deeper

**Task:** Color the points by continent.

```{r Scatterplot with color}
ggplot(data = gap07, aes(x = gdpPercap, y = lifeExp, color = continent)) +
  geom_point()
```

## Update your analysis

What if you wanted to now change your analysis 

- to subset for 1952

- plot life expectancy (`lifeExp`) vs. population (`pop`)

- and size the points by GPD (`gpdPercap`)
    - hint: add argument `size = gpdPercap` to your plotting code